Measurement Bias from Address Aliasing

### 2016-03-03 paper.tex
Disable bookmarks
Not allowed by pdf validation.
Change bibliography style
Reformat references.bib to resemble IEEE example. Disable clickable hyperlinks
and cross-references, as they are discouraged for publication.
Display full name of university and use ntnu email

% paper.tex
% Author: L. K. Melhus and R. E. Jensen
\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}
\usepackage{hyperref} % For PDF metadata
\usepackage[font=small]{caption}

@@

\author{\IEEEauthorblockN{Lars Kirkholt Melhus}
\IEEEauthorblockA{Dept. of Computer and Information Science (IDI)\\
NTNU, Norway\\
lars.kirkholt.melhus@gmail.com}
\and
\IEEEauthorblockN{Rune Erlend Jensen}
\IEEEauthorblockA{Dept. of Computer and Information Science (IDI)\\
NTNU, Norway\\
runeerle@idi.ntnu.no}
}

@@

% Bibliography
\bibliographystyle{abbrv}
\bibliography{references}

>>>>

% paper.tex
% Author: L. K. Melhus and R. E. Jensen
\documentclass[10pt, conference, compsocconf]{IEEEtran}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{tikz}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url} % Better line breaking of urls
\usepackage{lmodern} % Much clearer text
\usepackage[utf8]{inputenc}
\usepackage[font=small]{caption}

@@

\author{\IEEEauthorblockN{Lars Kirkholt Melhus}
\IEEEauthorblockA{Dept. of Computer and Information Science\\
Norwegian University of Science and Technology\\
Trondheim, Norway\\
larskirk@alumni.ntnu.no}
\and
\IEEEauthorblockN{Rune Erlend Jensen}
\IEEEauthorblockA{Dept. of Computer and Information Science\\
Norwegian University of Science and Technology\\
Trondheim, Norway\\
runeerle@idi.ntnu.no}
}

@@

% Bibliography
\bibliographystyle{IEEEtran}
\bibliography{references}
